---
title: "Parallel strategies in `simChef`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Parallel strategies in `simChef`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pcs.sim.pkg)
library(future)
```

Given the large amount of computation that simulation experiments require,
`simChef` uses the R package [`future`](https://future.futureverse.org/) to
distribute computation across available resources. Users must decide upon two
aspects of the distributed computation in order to effectively parallelize the
simulations: _what_ resources to use and _how_ to use them.

`simChef` is entirely agnostic to the answer to the _what_ question; any
resource that `future` supports is also supported. For example, to run your
simulation experiments on your local Linux, macOS, or Windows machine using all
but one of the cores, you might run:

```{r, plan-multisession, eval=FALSE}
n_workers <- availableCores() - 1
plan(multisession, workers = n_workers)
```

Once a `future` plan has been set, `simChef` will execute computation according
to the plan specified. To answer the _how_ question, consider `n` computational
"tasks" to be distributed across `p` parallel workers. Assuming each task takes
approximately the same amount of time to complete regardless of the worker
assigned to the task, then with `n=100` and `p=4` each worker should complete
around 25 of the tasks. In the ideal setting, the total time to complete the 100
tasks should be around 4 times lower than the time it takes one worker to
complete them, on average.

In more realistic scenarios, and especially in simulation experiments where
heterogeneous methods are compared in various diverse problem settings, tasks
are often much less uniform and different parallel strategies can have profound
implications for the overall running time. Therefore, it's important to
carefully decide how to package your tasks in order to take greatest advantage
of the available parallelism.

By default, `simChef` distributes computation across the available resources by
splitting up the simulation's replicates evenly across available workers,
answering the _how_ question. However, `simChef` gives the user more
fine-grained control over how computation is split across available resources by
setting the parallel strategy when calling `Experiment$fit()` or
`Experiment$run()` via the `parallel_strategy` argument. The possible values and
implications of `parallel_strategy` are listed in the table below:

+-----|-----+
| `parallel_strategy` | Parallelism |
+-----|-----|-----+
| `"reps"` | One task per simulation replicate |
+-----|-----|-----+
| `"dgps"` | One task per `DGP` objects in `Experiment` |
+-----|-----|-----+
|  `"methods"` | One task per `Method` objects in `Experiment` |
+-----|-----|-----+
| `c("reps", "dgps")` | One task per combination of replicates and `DGP` objects  |
+-----|-----|-----+
| `c("reps", "methods")` | One task per combination of replicates and `Method` objects  |
+-----|-----|-----+
| `c("dgps", "methods")` | One task per combination of `DGP` and `Method` objects  |
+-----|-----|-----+
| `c("reps", "dgps", "methods")` | One task per combination of replicates, `DGP` and `Method` objects |
+-----|-----+

The best parallel strategy is entirely dependent on the details of your
particular simulation experiment. In general, one should not have fewer tasks
than workers and should avoid `n>>p` very small tasks as the overhead of
distributing computation to workers may outweigh the benefits of parallelism.

```{r, parallel-ex}
n_workers <- availableCores() - 1
plan(multisession, workers = n_workers)

dgp_fun <- function(n, noise_level = 4) {
  X <- matrix(rnorm(n * 2), nrow=n)
  y <- cbind(1, X) %*% c(-8, 3, -1) + rnorm(n, sd = noise_level)
  return(list(X = X, y = y))
}

dgp1 <- create_dgp(dgp_fun, n = 200, noise_level = 1)
dgp2 <- create_dgp(dgp_fun, n = 400, noise_level = 2)

method_fun <- function(X, y, sleep = 0.001) {
  fit_summary <- lm(y ~ X) %>%
    broom::tidy()
  Sys.sleep(sleep)
  return(fit_summary)
}

method1 <- create_method(method_fun)
method2 <- create_method(method_fun, sleep=0.01)

experiment <- create_experiment(name = "base") %>%
  add_dgp(dgp1) %>%
  add_dgp(dgp2) %>%
  add_method(method1) %>%
  add_method(method2)

system.time(
  experiment$fit(n_reps = 100, parallel_strategy = c("reps", "dgps"))
)


```
