---
title: "`r params$sim_name`"
author: "`r params$author`"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::html_document
params:
  author: 
    label: "Author:"
    value: ""
  sim_name:
    label: "Simulation Experiment Name:"
    value: ""
  sim_path:
    label: "Path to Simulation Experiment Folder:"
    value: ""
  write_filename:
    label: "Output File:"
    value: ""
  show_code:
    label: "Show Code:"
    value: TRUE
  show_eval:
    label: "Show Evaluators:"
    value: TRUE
  show_viz:
    label: "Show Visualizers:"
    value: TRUE
  eval_order:
    label: "Order of Evaluators:"
    value: NULL
  viz_order:
    label: "Order of Visualizers:"
    value: NULL
  eval_cache:
    label: "Evaluators Cache Type:"
    value: ".rds"
  viz_cache:
    label: "Visualizers Cache Type:"
    value: ".rds"
  use_icons:
    label: "Use Icons:"
    value: TRUE
  use_vmodern:
    label: "Use vthemes::vmodern:"
    value: TRUE
  write:
    label: "Write File:"
    value: FALSE
  verbose:
    label: "Verbose Level:"
    value: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE,
  fig.align = "center",
  fig.pos = "H",
  fig.height = 12,
  fig.width = 10
)

options(
  width = 10000,
  knitr.kable.NA = "NA"
)

# scrollable text output
local({
  hook_output <- knitr::knit_hooks$get("output")
  knitr::knit_hooks$set(output = function(x, options) {
    if (!is.null(options$max.height)) {
      options$attr.output <- c(
        options$attr.output,
        sprintf('style="max-height: %s;"', options$max.height)
      )
    }
    hook_output(x, options)
  })
})

chunk_idx <- 1
doc_dir <- file.path(params$sim_path, "docs")
write_filename <- params$write_filename
```

```{r helper-funs}

#' Wrap text/code in knitr code chunk string
#'
#' @param code String of code to wrap in knitr code chunk
#' @param chunk_args String of arguments to place in the knitr code chunk header
#' @return String of code, wrapped inside the knitr code chunk ``` markers
write_code_chunk <- function(code = "", chunk_args = "") {
  sprintf("\n```{r, %s}\n%s\n```\n", chunk_args, code)
}

#' Write text to vector (write_flag = TRUE) or to console (write_flag = FALSE)
#'
#' @param ... Text to write to vector or to console
#' @param old_text Previous text to append to when writing to a vector
#' @param write_flag Boolean indicating whether to write text to a vector
#'   (write_flag = TRUE) or to console (write_flag = FALSE)
#' @return If write_flag = TRUE, returns vector of text. Otherwise, text is
#'   written to console via `cat()`.
write <- function(..., old_text = NULL, write_flag) {
  if (write_flag) {
    return(c(old_text, ...))
  } else {
    dots_list <- list(...) |>
      purrr::map(
        function(x) {
          if (stringr::str_detect(x, "`r .*`")) {
            # run r code before printing results in cat()
            out <- stringr::str_replace(
              x, "`r .*`",
              eval(parse(text = stringr::str_extract(x, "(?<=`r )(.*?)(?=`)")))
            )
          } else {
            out <- x
          }
          return(out)
        }
      )
    do.call(cat, args = c(dots_list, list(sep = "")))
  }
}

#' Write text to file
#'
#' @param path Path to output file
#' @param ... Text to output to file
write_to_file <- function(path, ...) {
  storelines <- readLines(path)
  storelines <- c(storelines, ...)
  writeLines(storelines, path)
}

#' Get order of objects to display
#'
#' @param obj_names Vector of all object names that need to be displayed.
#' @param obj_order Vector of object names in the desired appearance order.
#' @return Vector of object names in the order in which they will be displayed.
get_object_order <- function(obj_names, obj_order = NULL) {
  if (is.null(obj_order)) {
    return(obj_names)
  } else {
    return(intersect(obj_order, obj_names))
  }
}

#' Get all experiments under a given directory name
#'
#' @param dir_name name of directory
#' @return list of named experiments
get_descendants <- function(dir_name) {
  experiments <- list()
  for (d in list.dirs(dir_name)) {
    if (file.exists(file.path(d, "experiment.rds"))) {
      if (identical(d, params$sim_path)) {
        exp_name <- "Base"
      } else {
        exp_name <- stringr::str_replace_all(
          stringr::str_remove(d, paste0(params$sim_path, "/")),
          "/", " - "
        )
      }
      experiments[[exp_name]] <- readRDS(file.path(d, "experiment.rds"))
    }
  }
  return(experiments)
}

#' Check if experiment exists
#'
#' @param dir_name name of directory or vector thereof
#' @param recursive logical; if TRUE, checks if experiment exists under the
#'   given directory(s); if FALSE, checks if any experiment exists under the
#'   directory(s) and its descendants
#' @return TRUE if experiment exists and FALSE otherwise
experiment_exists <- function(dir_name, recursive = FALSE) {
  res <- purrr::map_lgl(
    dir_name,
    function(d) {
      if (!recursive) {
        exp_fname <- file.path(d, "experiment.rds")
        return(file.exists(exp_fname))
      } else {
        descendants <- get_descendants(d)
        return(length(descendants) > 0)
      }
    }
  )
  return(any(res))
}

#' Print renv lockfile info
#' 
#' @param renv_lockfile renv lockfile object from [renv::lockfile_read()]
#' @param what part of renv lockfile to print; must be one of "R" or "packages"
#' @param print_table logical; whether to print as a nice table (TRUE) or 
#'   simply using the `print` method.
#' @return renv lockfile info
print_renv <- function(renv_lockfile, 
                       what = c("R", "Packages"),
                       print_table = FALSE) {
  what <- match.arg(what)
  if (what == "R") {
    if (print_table) {
      tab <- tibble::tibble(
        `R Version` = renv_lockfile$R$Version, 
        Repositories = paste(
          names(renv_lockfile$R$Repositories), 
          " (", renv_lockfile$R$Repositories, ")", 
          sep = "", collapse = "<br>"
        )
      ) |> 
        vthemes::pretty_DT(
          rownames = FALSE, options = list(dom = "t", ordering = FALSE)
        )
      return(tab)
    } else {
      return(renv_lockfile$R)
    }
  } else {
    if (print_table) {
      tab <- tibble::tibble(
        `Package Name` = purrr::map_chr(
          renv_lockfile$Packages, 
          function(.x) if (!is.null(.x$Package)) .x$Package else "N/A"
        ),
        `Version` = purrr::map_chr(
          renv_lockfile$Packages,
          function(.x) if (!is.null(.x$Version)) .x$Version else "N/A"
        ),
        `Source` = purrr::map_chr(
          renv_lockfile$Packages,
          function(.x) if (!is.null(.x$Source)) .x$Source else "N/A"
        ),
        `Repository` = purrr::map_chr(
          renv_lockfile$Packages,
          function(.x) {
            if (!is.null(.x$Repository)) {
              .x$Repository
            } else if (!is.null(.x$RemoteUrl)) {
              .x$RemoteUrl
            } else if (.x$Source == "GitHub") {
              sprintf("https://github.com/%s/%s", .x$RemoteUsername, .x$RemoteRepo)
            } else {
              "N/A"
            }
          }
        ),
        `Requirements` = purrr::map_chr(
          renv_lockfile$Packages, ~ paste(.x$Requirements, collapse = ", ")
        )
      ) |> 
        vthemes::pretty_DT(rownames = FALSE)
      return(tab)
    } else {
      return(renv_lockfile$Packages)
    }
  }
}

#' Displays content for specified part of recipe
#'
#' @param field_name part of recipe to show; must be one of "dgp", "method",
#'   "evaluator", or "visualizer"
#' @param write_flag Boolean indicating whether to write text to a vector
#'   (write_flag = TRUE) or to console (write_flag = FALSE)
#' @return content for recipe
show_recipe <- function(field_name = c(
                          "dgp", "method", "evaluator", "visualizer", "renv"
                        ),
                        write_flag = FALSE) {
  field_name <- match.arg(field_name)
  func_name <- dplyr::case_when(
    field_name == "evaluator" ~ "eval",
    field_name == "visualizer" ~ "viz",
    TRUE ~ field_name
  )
  recipe <- c()
  if (field_name == "renv") {
    if (!rlang::is_installed("renv")) {
      return(NULL)
    }
    renv_lockfile <- tryCatch(
      renv::lockfile_read(),
      error = function(e) NULL
    )
    if (is.null(renv_lockfile)) {
      return(NULL)
    }
    
    sec_header <- "\n\n## %s {.tabset .tabset-pills .tabset-square}\n\n"
    subsec_header <- "\n\n### %s\n\n"
    subsubsec_header <- "\n\n#### %s {.tabset .tabset-pills .tabset-circle .tabset-recipe}\n\n"
    showtype_header <- "\n\n##### %s\n\n"
    if (params$use_icons) {
      if (params$use_vmodern) {
        table_label <- "`r fontawesome::fa('table', fill = 'white')`"
        print_label <- "`r fontawesome::fa('code', fill = 'white')`"
      } else {
        table_label <- "`r fontawesome::fa('table')`"
        print_label <- "`r fontawesome::fa('code')`"
      }
    } else {
      table_label <- "Abridged Table"
      print_label <- "Full Output"
    }
    
    recipe <- write(
      sprintf(sec_header, "R Environment"),
      sprintf(subsec_header, "R/Packages"),
      old_text = recipe, write_flag = write_flag
    )
    
    for (what in c("R", "Packages")) {
      recipe <- write(
        sprintf(subsubsec_header, what),
        old_text = recipe, write_flag = write_flag
      )
      
      if (params$use_vmodern) {
          recipe <- write(
            "\n\n<div class='panel panel-default padded-panel'>\n\n",
            old_text = recipe, write_flag = write_flag
          )
      }
      
      # table
      recipe <- write(
        sprintf(showtype_header, table_label),
        old_text = recipe, write_flag = write_flag
      )
      if (write_flag) {
        recipe <- write_code_chunk(
          sprintf(
            "print_renv(renv::lockfile_read(), '%s', print_table = TRUE)", what
          ),
          chunk_args = "results = 'asis'"
        ) |>
          write(old_text = recipe, write_flag = write_flag)
      } else {
        vthemes::subchunkify(
          print_renv(renv_lockfile, what, print_table = TRUE), chunk_idx
        )
        chunk_idx <<- chunk_idx + 1
      }
      
      # print output
      recipe <- write(
        sprintf(showtype_header, print_label),
        old_text = recipe, write_flag = write_flag
      )
      if (write_flag) {
        recipe <- write_code_chunk(
          sprintf(
            "print_renv(renv::lockfile_read(), '%s', print_table = FALSE)", what
          ),
          chunk_args = "max.height='700px'"
        ) |>
          write(old_text = recipe, write_flag = write_flag)
      } else {
        vthemes::subchunkify(
          print_renv(renv_lockfile, what, print_table = FALSE), chunk_idx,
          other_args = "max.height='700px'"
        )
        chunk_idx <<- chunk_idx + 1
      }
      
      if (params$use_vmodern) {
        recipe <- write(
          "\n\n</div>\n\n", old_text = recipe, write_flag = write_flag
        )
      }
    }
    
    # renv diagnostics
    recipe <- write(
      sprintf(subsec_header, "Full renv Diagnostics"),
      old_text = recipe, write_flag = write_flag
    )
      
    if (params$use_vmodern) {
        recipe <- write(
          "\n\n<div class='panel panel-default padded-panel'>\n\n",
          old_text = recipe, write_flag = write_flag
        )
    }
    
    if (write_flag) {
      recipe <- write_code_chunk(
        code = "renv::diagnostics()",
        chunk_args = "max.height='700px'"
      ) |>
        write(old_text = recipe, write_flag = write_flag)
    } else {
      vthemes::subchunkify(
        renv::diagnostics(), chunk_idx,
        other_args = "max.height='700px'"
      )
      chunk_idx <<- chunk_idx + 1
    }
    
    if (params$use_vmodern) {
      recipe <- write(
        "\n\n</div>\n\n", old_text = recipe, write_flag = write_flag
      )
    }
  } else {
    descendants <- get_descendants(dir_name = params$sim_path)
    objs <- purrr::map(descendants, ~ .x[[paste0("get_", field_name, "s")]]())
    obj_names <- unique(purrr::reduce(sapply(objs, names), c))
    obj_header <- "\n\n### %s {.tabset .tabset-pills .tabset-circle .tabset-recipe}\n\n"
    showtype_header <- "\n\n#### %s {.tabset .tabset-pills}\n\n"
    exp_header <- "\n\n##### %s \n\n"
  
    if (params$use_icons) {
      if (params$use_vmodern) {
        description_label <- "`r fontawesome::fa('readme', fill = 'white')`"
        code_label <- "`r fontawesome::fa('code', fill = 'white')`"
      } else {
        description_label <- "`r fontawesome::fa('readme')`"
        code_label <- "`r fontawesome::fa('code')`"
      }
    } else {
      description_label <- "Description"
      code_label <- "Code"
    }
  
    if (all(sapply(objs, length) == 0)) {
      if (write_flag) {
        return("N/A")
      } else {
        return(cat("N/A"))
      }
    }
  
    for (idx in 1:length(obj_names)) {
      obj_name <- obj_names[idx]
      description_fpath <- file.path(
        doc_dir, paste0(field_name, "s"), paste0(obj_name, ".md")
      )
      
      if (params$use_vmodern) {
        recipe <- write(
          "\n\n<div class='panel panel-default padded-panel'>\n\n",
          old_text = recipe, write_flag = write_flag
        )
      }
  
      recipe <- write(
        sprintf(obj_header, obj_name),
        sprintf(showtype_header, description_label),
        paste_md(description_fpath),
        old_text = recipe, write_flag = write_flag
      )
  
      if (params$show_code) {
        recipe <- write(
          sprintf(showtype_header, code_label),
          old_text = recipe, write_flag = write_flag
        )
  
        keep_objs <- purrr::compact(purrr::map(objs, obj_name))
        is_identical <- all(
          purrr::map_lgl(keep_objs, ~ isTRUE(check_equal(.x, keep_objs[[1]])))
        )
        for (exp in names(keep_objs)) {
          obj <- keep_objs[[exp]]
          if (!is_identical) {
            recipe <- write(
              sprintf(exp_header, exp),
              old_text = recipe, write_flag = write_flag
            )
          }
  
          recipe <- write(
            "\n\n**Function**\n\n",
            old_text = recipe, write_flag = write_flag
          )
          if (write_flag) {
            recipe <- sprintf(
              "show_recipe(%s_objs, '%s', '%s', what = 'function')",
              func_name, obj_name, exp
            ) |>
              write_code_chunk(chunk_args = "max.height='200px'") |>
              write(old_text = recipe, write_flag = write_flag)
          } else {
            vthemes::subchunkify(
              obj[[paste0(func_name, "_fun")]], chunk_idx,
              other_args = "max.height='200px'"
            )
            chunk_idx <<- chunk_idx + 1
          }
  
          recipe <- write(
            "\n\n**Input Parameters**\n\n",
            old_text = recipe, write_flag = write_flag
          )
          if (write_flag) {
            recipe <- sprintf(
              "show_recipe(%s_objs, '%s', '%s', what = 'parameters')",
              func_name, obj_name, exp
            ) |>
              write_code_chunk(chunk_args = "max.height='200px'") |>
              write(old_text = recipe, write_flag = write_flag)
          } else {
            vthemes::subchunkify(
              obj[[paste0(func_name, "_params")]], chunk_idx,
              other_args = "max.height='200px'"
            )
            chunk_idx <<- chunk_idx + 1
          }
  
          if (is_identical) {
            break
          }
        }
      }
  
      if (params$use_vmodern) {
        recipe <- write(
          "\n\n</div>\n\n", old_text = recipe, write_flag = write_flag
        )
      }
    }
  }

  return(recipe)
}

#' Reads in file if it exists and returns NULL if the file does not exist
#' 
#' @description If filetype is ".rds", the file is read in using readRDS(). 
#'   Otherwise, the file is read in using data.table::fread().
#'
#' @param filename name of file (with file extension) to try reading in
#' @param filetype file extension
#' @param experiment experiment object
#' @param experiment_save_dir directory where experiment results are saved
#' @param field_name one of "evaluator" or "visualizer"
#' @return output of experiment results if the file exists and NULL otherwise
get_results <- function(filename, filetype = ".rds",
                        experiment, experiment_save_dir = NULL,
                        field_name = c("evaluator", "visualizer")) {
  field_name <- match.arg(field_name)
  if (field_name == "evaluator") {
    save_in_bulk <- experiment$get_save_in_bulk()[["eval"]]
  } else if (field_name == "visualizer") {
    save_in_bulk <- experiment$get_save_in_bulk()[["viz"]]
  }
  results <- NULL
  if (save_in_bulk) {
    if (file.exists(filename)) {
      if (filetype == ".rds") {
        results <- readRDS(filename)
      } else {
        results <- data.table::fread(results)
      }
    }
  } else {
    if (is.null(experiment_save_dir)) {
      stop("experiment_save_dir must be provided if save_in_bulk is FALSE")
    }
    if (field_name == "evaluator") {
      obj_names <- names(experiment$get_evaluators())
      obj_dirname <- file.path(experiment_save_dir, "eval_results")
    } else if (field_name == "visualizer") {
      obj_names <- names(experiment$get_visualizers())
      obj_dirname <- file.path(experiment_save_dir, "viz_results")
    }
    if (length(obj_names) == 0) {
      return(NULL)
    }
    names(obj_names) <- obj_names
    results <- purrr::map(
      obj_names, 
      function(obj_name) {
        obj_fname <- file.path(obj_dirname, sprintf("%s%s", obj_name, filetype))
        if (file.exists(obj_fname)) {
          if (filetype == ".rds") {
            results <- readRDS(obj_fname)
          } else {
            results <- data.table::fread(obj_fname)
          }
        } else {
          results <- NULL
        }
        return(results)
      } 
    ) |> 
      purrr::compact()
  }
  
  return(results)
}

#' Reads in list of image result files
#' 
#' @param filenames vector of filenames (without file extension) to read in
#' @param filetype file extension
#' @return list of image results, wrapped as knitr::include_graphics() objects
get_image_results <- function(filenames, filetype) {
  purrr::map(
    filenames,
    function(f) {
      if (file.exists(sprintf("%s%s", f, filetype))) {
        return(knitr::include_graphics(sprintf("%s%s", f, filetype)))
      } else {
        return(NULL)
      }
    }
  ) |> 
    setNames(basename(filenames)) |> 
    purrr::compact()
}

#' Get results from experiment
#' 
#' @param dir_name name of directory
#' @param show_eval logical; whether or not to show evaluators
#' @param show_viz logical; whether or not to show visualizers
#' @param eval_cache file extension for cached evaluator results to read in.
#'   Typically ".rds" or "none", but can be any file extension where
#'   evaluator results are stored as `eval_results.ext` and can be read in
#'   using `data.table::fread(eval_results.ext)`. If "none", evaluator results
#'   are computed using the experiment via `evaluate_experiment()`.
#' @param viz_cache file extension for cached visualizer results to read in.
#'   Typically ".rds" or "none", but can be any (image) file extension 
#'   (e.g., "png", "jpg") where the visualizer results have been previously 
#'   stored as separate `{visualizer_name}.ext` images (e.g., using
#'   `export_visualizers()`). If "none", visualizer results are computed using
#'   the experiment via `visualize_experiment()`.
get_exp_results <- function(dir_name, 
                            show_eval = TRUE, show_viz = TRUE,
                            eval_cache = ".rds", viz_cache = ".rds") {
  
  exp_fname <- file.path(dir_name, "experiment.rds")
  eval_fname <- file.path(dir_name, sprintf("eval_results%s", eval_cache))
  viz_fname <- file.path(dir_name, sprintf("viz_results%s", viz_cache))

  exp <- readRDS(exp_fname)
  fit_results <- NULL
  eval_results <- NULL
  viz_results <- NULL
  if ((eval_cache != "none") && (viz_cache == ".rds")) {
    if (show_eval) {
      eval_results <- get_results(
        filename = eval_fname, 
        filetype = eval_cache, 
        experiment = exp, 
        experiment_save_dir = dir_name,
        field_name = "evaluator"
      )
    }
    if (show_viz) {
      viz_results <- get_results(
        filename = viz_fname, 
        filetype = viz_cache, 
        experiment = exp, 
        experiment_save_dir = dir_name,
        field_name = "visualizer"
      )
    }
  } else {
    if (show_eval) {
      if (eval_cache == "none") {
        fit_results <- suppressMessages(get_cached_results(exp, "fit"))
        if (is.null(fit_results)) {
          stop("Cannot set eval_cache = 'none' since no cached fit results found. Perhaps try setting eval_cache = '.rds' instead.")
        }
        eval_results <- evaluate_experiment(exp, fit_results)
      } else {
        eval_results <- get_results(
          filename = eval_fname, 
          filetype = eval_cache, 
          experiment = exp, 
          experiment_save_dir = dir_name,
          field_name = "evaluator"
        )
      }
    }
    if (show_viz) {
      if (viz_cache == ".rds") {
        viz_results <- get_results(
          filename = viz_fname, 
          filetype = viz_cache, 
          experiment = exp, 
          experiment_save_dir = dir_name,
          field_name = "visualizer"
        )
      } else if (viz_cache == "none") {
        if (is.null(fit_results)) {
          fit_results <- suppressMessages(get_cached_results(exp, "fit"))
          if (is.null(fit_results)) {
            stop("Cannot set viz_cache = 'none' since no cached fit results found. Perhaps try setting viz_cache = '.rds' instead.")
          }
        }
        if (is.null(eval_results)) {
          eval_results <- suppressMessages(get_cached_results(exp, "eval"))
          if (is.null(eval_results)) {
            eval_results <- evaluate_experiment(exp, fit_results)
          }
        }
        viz_results <- visualize_experiment(exp, fit_results, eval_results)
      } else {
        viz_results <- get_image_results(
          file.path(dir_name, names(exp$get_visualizers())), viz_cache
        )
      }
    }
  }
  results <- list(
    exp = exp,
    eval_results = eval_results,
    viz_results = viz_results
  )
  return(results)
}

#' Displays output (both from evaluate() and visualize()) from saved results under
#' a specified directory
#'
#' @param dir_name name of directory
#' @param depth integer; depth of directory from parent/base experiment's folder
#' @param base logical; whether or not this is a base experiment
#' @param show_header logical; whether or not to show section header
#' @param verbose integer; 0 = no messages; 1 = print out directory name only;
#'   2 = print out directory name and name of evaluators/visualizers
#' @param write_flag Boolean indicating whether to write text to a vector
#'   (write_flag = TRUE) or to console (write_flag = FALSE)
#' @return content results from evaluate() and visualize() from the experiment
show_results <- function(dir_name, depth, base = FALSE, show_header = TRUE,
                         verbose = 1, write_flag = FALSE) {
  if (verbose >= 1) {
    inform(paste0(paste(rep("*", depth), collapse = ""), basename(dir_name)))
  }

  if (depth == 1) {
    header_template <- "\n\n%s %s {.tabset .tabset-pills .tabset-vmodern}\n\n"
  } else {
    if (base || !experiment_exists(dir_name)) {
      header_template <- "\n\n%s %s {.tabset .tabset-pills}\n\n"
    } else {
      header_template <- "\n\n%s %s {.tabset .tabset-pills .tabset-circle}\n\n"
    }
  }

  results <- c()
  if (show_header) {
    results <- sprintf(
      header_template,
      paste(rep("#", depth), collapse = ""),
      basename(dir_name)
    ) |>
      write(old_text = results, write_flag = write_flag)
  }

  if (base) {
    results <- sprintf(
      "\n\n%s Base - %s {.tabset .tabset-pills .tabset-circle}\n\n",
      paste(rep("#", depth + 1), collapse = ""),
      basename(dir_name)
    ) |>
      write(old_text = results, write_flag = write_flag)
    depth <- depth + 1
  }

  showtype_template <- paste0(
    "\n\n", paste(rep("#", depth + 1), collapse = ""), " %s\n\n"
  )
  figname_template <- paste0(
    "\n\n", paste(rep("#", depth + 2), collapse = ""), " %s\n\n"
  )
  invisible_header <- paste0(
    "\n\n", paste(rep("#", depth + 3), collapse = ""),
    " {.tabset .tabset-pills}\n\n"
  )
  plt_template <- paste0(
    "\n\n", paste(rep("#", depth + 4), collapse = ""), " %s\n\n"
  )

  if (params$use_icons) {
    if (params$use_vmodern) {
      evaluator_label <- "`r fontawesome::fa('table', fill = 'white')`"
      visualizer_label <- "`r fontawesome::fa('chart-bar', fill = 'white')`"
      code_label <- "`r fontawesome::fa('code', fill = 'white')`"
    } else {
      evaluator_label <- "`r fontawesome::fa('table')`"
      visualizer_label <- "`r fontawesome::fa('chart-bar')`"
      code_label <- "`r fontawesome::fa('code')`"
    }
  } else {
    evaluator_label <- "Evaluators"
    visualizer_label <- "Visualizers"
    code_label <- "Varying Parameters"
  }

  exp_results <- get_exp_results(
    dir_name, 
    show_eval = params$show_eval, show_viz = params$show_viz,
    eval_cache = params$eval_cache, viz_cache = params$viz_cache
  )
  exp <- exp_results$exp
  eval_results <- exp_results$eval_results
  viz_results <- exp_results$viz_results

  if (write_flag && (params$show_eval || params$show_viz)) {
    results <- sprintf(
      "results <- get_exp_results(\n  '%s', show_eval = %s, show_viz = %s, eval_cache = '%s', viz_cache = '%s'\n)",
      dir_name, 
      params$show_eval, params$show_viz,
      params$eval_cache, params$viz_cache
    ) |>
      write_code_chunk(chunk_args = "results = 'asis'") |>
      write(old_text = results, write_flag = write_flag)
  }
  
  if (!is.null(eval_results) && params$show_eval) {
    results <- write(
      sprintf(showtype_template, evaluator_label),
      old_text = results, write_flag = write_flag
    )

    eval_names <- get_object_order(names(eval_results), params$eval_order)
    for (eval_name in eval_names) {
      evaluator <- exp$get_evaluators()[[eval_name]]
      if (evaluator$doc_show) {
        if (verbose >= 1) {
          inform(paste0(paste(rep(" ", depth + 1), collapse = ""), eval_name))
        }
        results <- write(
          sprintf(figname_template, eval_name),
          old_text = results, write_flag = write_flag
        )
        if (is.null(evaluator$doc_nrows)) {
          eval_results_show <- eval_results[[eval_name]]
        } else {
          keep_rows <- 1:min(evaluator$doc_nrows, nrow(eval_results[[eval_name]]))
          eval_results_show <- eval_results[[eval_name]][keep_rows, ]
          if (nrow(eval_results[[eval_name]]) > evaluator$doc_nrows) {
            omitted_nrows <- nrow(eval_results[[eval_name]]) - evaluator$doc_nrows
            results <- write(
              sprintf(
                "Showing preview of %s results. %s rows have been omitted.\n\n",
                eval_name, omitted_nrows
              ),
              old_text = results, write_flag = write_flag
            )
          }
        }
        if (write_flag) {
          results <- sprintf(
            "show_results(results, '%s', 'evaluator')", eval_name
          ) |>
            write_code_chunk(chunk_args = "results = 'asis'") |>
            write(old_text = results, write_flag = write_flag)
        } else {
          do.call(
            vthemes::pretty_DT,
            c(list(eval_results_show), evaluator$doc_options)
          ) |>
            vthemes::subchunkify(i = chunk_idx)
          chunk_idx <<- chunk_idx + 1
        }
      }
    }
  }

  if (!is.null(viz_results) && params$show_viz) {
    results <- write(
      sprintf(showtype_template, visualizer_label),
      old_text = results, write_flag = write_flag
    )

    viz_names <- get_object_order(names(viz_results), params$viz_order)
    for (viz_name in viz_names) {
      visualizer <- exp$get_visualizers()[[viz_name]]
      if (visualizer$doc_show) {
        if (verbose >= 1) {
          inform(paste0(paste(rep(" ", depth + 1), collapse = ""), viz_name))
        }
        results <- write(
          sprintf(figname_template, viz_name),
          invisible_header,
          old_text = results, write_flag = write_flag
        )
        plts <- viz_results[[viz_name]]
        if (!inherits(plts, "list")) {
          plts <- list(plt = plts)
        }
        if (is.null(names(plts))) {
          names(plts) <- 1:length(plts)
        }
        for (plt_name in names(plts)) {
          if (length(plts) != 1) {
            results <- write(
              sprintf(plt_template, plt_name),
              old_text = results, write_flag = write_flag
            )
          }
          plt <- plts[[plt_name]]
          is_plot <- inherits(plt, "plotly") || 
            inherits(plt, "gg") || 
            inherits(plt, "ggplot") ||
            inherits(plt, "knit_image_paths")
          
          if (params$use_vmodern && is_plot) {
            chunk_args <- "fig.height = %s, fig.width = %s, out.width = '100%%', add.panel = TRUE"
            add_class <- "panel panel-default padded-panel"
          } else {
            chunk_args <- "fig.height = %s, fig.width = %s, out.width = '100%%'"
            add_class <- NULL
          }
          
          if (write_flag) {
            results <- sprintf(
              "show_results(results, '%s', 'visualizer')", viz_name
            ) |>
              write_code_chunk(
                chunk_args = sprintf(
                  chunk_args,
                  visualizer$doc_options$height, visualizer$doc_options$width
                )
              ) |>
              write(old_text = results, write_flag = write_flag)
          } else {
            vthemes::subchunkify(plt,
              i = chunk_idx,
              fig_height = visualizer$doc_options$height,
              fig_width = visualizer$doc_options$width,
              other_args = "out.width = '100%'", 
              add_class = add_class
            )
            chunk_idx <<- chunk_idx + 1
          }
        }
      }
    }
  }

  if (!is.null(exp) && params$show_code) {
    if ((length(exp$get_vary_across()$dgp) != 0) ||
        (length(exp$get_vary_across()$method) != 0)) {
      results <- write(
        sprintf(showtype_template, code_label),
        "\n\n**Parameter Values**\n\n",
        old_text = results, write_flag = write_flag
      )
      if (write_flag) {
        results <- c("show_results(results, NULL, 'vary_params')") |>
          write_code_chunk(chunk_args = "max.height='200px'") |>
          write(old_text = results, write_flag = write_flag)
      } else {
        vthemes::subchunkify(exp$get_vary_across(),
          chunk_idx,
          other_args = "max.height='200px'"
        )
        chunk_idx <<- chunk_idx + 1
      }
    }
  }

  return(results)
}

#' Displays output of experiment for all of its (saved) descendants
#'
#' @param dir_name name of parent experiment directory
#' @param depth placeholder for recursion; should not be messed with
#' @param write_flag Boolean indicating whether to write text to a file
#'   (write_flag = TRUE) or to console (write_flag = FALSE)
#' @param write_filename Name of file to write to if write_flag = TRUE
#' @param ... other arguments to pass into show_results()
show_descendant_results <- function(dir_name, depth = 1, write_flag = FALSE,
                                    write_filename = NULL, ...) {
  children <- list.dirs(dir_name, recursive = FALSE)
  if (length(children) == 0) {
    return()
  }
  for (child_idx in 1:length(children)) {
    child <- children[child_idx]
    if (!experiment_exists(child, recursive = TRUE)) {
      next
    }
    if (experiment_exists(child, recursive = FALSE) &&
      (experiment_exists(list.dirs(child, recursive = TRUE)[-1]) ||
        (depth == 1))) {
      base <- TRUE
    } else {
      base <- FALSE
    }
    results <- show_results(child, depth, base, write_flag = write_flag, ...)
    if (write_flag) {
      write_to_file(path = write_filename, results)
    }
    show_descendant_results(child, depth + 1, write_flag, write_filename, ...)
  }
}

#' Clean output file (e.g., remove excessive blank lines)
#'
#' @param path Path to output file
clean_file <- function(path) {
  storelines <- readLines(path)
  rle_out <- rle(storelines == "")
  line_ids <- which((rle_out$lengths > 2) & rle_out$values)
  keep_lines <- rep(TRUE, length(storelines))
  for (line_id in line_ids) {
    num_blank <- rle_out$lengths[line_id]
    line_ptr <- sum(rle_out$lengths[1:line_id])
    # only allow for max of two consecutive blank lines
    keep_lines[(line_ptr - num_blank + 3):line_ptr] <- FALSE
  }
  writeLines(storelines[keep_lines], path)
}

#' Insert lines to add extra resources (css/js) for simChef R Markdown theme
#' 
#' @param path Path to output file
insert_simChef_resources <- function(path) {
  storelines <- readLines(path)
  pattern <- "<Insert extra simChef resources here>"
  replace <- sprintf(
    '<script src="%s"></script>\n\n<link rel="stylesheet" href="%s">', 
    system.file("rmd", "js", "simchefNavClass.js",
                package = utils::packageName()),
    system.file("rmd", "css", "simchef.css",
                package = utils::packageName())
  ) 
  storelines[storelines == pattern] <- replace
  writeLines(storelines, path)
}

#' Remove lines with simChef R Markdown theme-specific code
#' 
#' @param path Path to output file
remove_simChef_resources <- function(path) {
  storelines <- readLines(path)
  
  pattern <- "add.panel = function"
  line_id <- which(stringr::str_detect(storelines, pattern))
  remove_lines <- (line_id - 2):(line_id + 5)
  storelines <- storelines[-remove_lines]
  
  pattern <- "<Insert extra simChef resources here>"
  remove_lines <- which(stringr::str_detect(storelines, pattern))
  storelines <- storelines[-remove_lines]
  
  writeLines(storelines, path)
}

```

```{r}
if (params$write) {
  if (params$use_vmodern) {
    insert_simChef_resources(write_filename)
  } else {
    remove_simChef_resources(write_filename)
  }
} else {
  if (params$use_vmodern) {
    HTML('<script src="js/simchefNavClass.js"></script>\n\n<link rel="stylesheet" href="css/simchef.css">')
  }
}
```


# Simulation Experiment Recipe {.tabset .tabset-vmodern}

## Objectives

```{r objectives, results = "asis"}
if (params$use_vmodern) {
  objectives <- write(
    "\n\n<div class='panel panel-default padded-panel'>\n\n",
    paste_md(file.path(doc_dir, "objectives.md")),
    "\n\n</div>\n\n",
    write_flag = params$write
  )
} else {
  objectives <- write(
    paste_md(file.path(doc_dir, "objectives.md")),
    write_flag = params$write
  )
}
if (params$write) {
  write_to_file(path = write_filename, "\n\n## Objectives\n\n", objectives)
}
```

## Data Generation

```{r dgps, results = "asis"}
dgp_recipe <- show_recipe(field_name = "dgp", write_flag = params$write)
if (params$write) {
  write_to_file(path = write_filename, "\n\n## Data Generation\n\n", dgp_recipe)
}
```

## Methods

```{r methods, results = "asis"}
method_recipe <- show_recipe(field_name = "method", write_flag = params$write)
if (params$write) {
  write_to_file(path = write_filename, "\n\n## Methods \n\n", method_recipe)
}
```

## Evaluation

```{r evaluators, results = "asis"}
eval_recipe <- show_recipe(field_name = "evaluator", write_flag = params$write)
if (params$write) {
  write_to_file(path = write_filename, "\n\n### Evaluation\n\n", eval_recipe)
}
```

## Visualizations

```{r visualizers, results = "asis"}
viz_recipe <- show_recipe(field_name = "visualizer", write_flag = params$write)
if (params$write) {
  write_to_file(path = write_filename, "\n\n## Visualizations\n\n", viz_recipe)
}
```

```{r renv, results = "asis"}
renv_recipe <- show_recipe(field_name = "renv", write_flag = params$write)
if (params$write) {
  write_to_file(path = write_filename, renv_recipe)
}
```

```{r res, results = "asis"}
if (params$verbose > 0) {
  inform(sprintf("Creating R Markdown report for %s...", params$sim_name))
}

# show results
if (experiment_exists(params$sim_path)) {
  base_header <- write(
    sprintf("\n\n# Base %s \n\n", params$sim_name),
    "\n\n## {.tabset .tabset-pills .tabset-circle}\n\n",
    write_flag = params$write
  )
  base_results <- show_results(
    params$sim_path,
    depth = 2, base = FALSE, show_header = FALSE,
    verbose = params$verbose, write_flag = params$write
  )

  if (params$write) {
    write_to_file(path = write_filename, base_header, base_results)
  }
}

show_descendant_results(
  params$sim_path,
  verbose = params$verbose,
  write_flag = params$write, 
  write_filename = write_filename
)
```



```{r}
if (params$write) {
  clean_file(path = write_filename)
}
```
